Concurrent Programming with CXL

### 2020-07-03 book/paper.tex
Added links to sources

@@

\begin{figure}
\begin{code}
\cxlsource{triangle}
\end{code}
\caption{[triangle.cxl] Computing triangle numbers.}
\label{fig:triangle}
\end{figure}

@@

\begin{figure}[h]
\begin{code}
\cxlsource{Up}
\end{code}
\caption{[Up.cxl] Incrementing twice in parallel.}
\label{fig:inc}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{UpEnter}
\end{code}
\caption{[UpEnter.cxl] Broken attempt at fixing the code of Figure~\ref{fig:inc}.}
\label{fig:incenter}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{csbarebones}
\end{code}
\caption{[csbarebones.cxl] A bare bones critical section with two processes.}
\label{fig:csbarebones}
\end{figure}

\begin{figure}
\begin{code}
\cxlsource{cs}
\end{code}
\caption{[cx.cxl] CXL model of a critical section.}
\label{fig:cs}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{naiveLock}
\end{code}
\caption{[naiveLock.cxl] Na\"{\i}ve implementation of a shared lock.}
\label{fig:uplock}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{naiveFlags}
\end{code}
\caption{[naiveFlags.cxl] Na\"{\i}ve use of flags to solve mutual exclusion.}
\label{fig:upflags}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{naiveTurn}
\end{code}
\caption{[naiveTurn.cxl] Na\"{\i}ve use of turn variable to solve mutual exclusion.}
\label{fig:upturn}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{Peterson}
\end{code}
\caption{[Peterson.cxl] Peterson's Algorithm}
\label{fig:peterson}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{PetersonInductive}
\end{code}
\caption{[PetersonInductive.cxl] Peterson's Algorithm with Inductive Invariant}
\label{fig:petersonproof}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{csonebit}
\end{code}
\caption{[csonebit.cxl] Mutual exclusion using a flag per process.}
\label{fig:csonebit}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{PetersonMethod}
\end{code}
\caption{[PetersonMethod.cxl] Peterson's Algorithm accessed through methods.}
\label{fig:petersonmethods}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{spinlock}
\end{code}
\caption{[spinlock.cxl] Mutual Exclusion using a ``spinlock'' based on test-and-set.}
\label{fig:tas}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{spinlockInv}
\end{code}
\caption{[spinlockInv.cxl] Checking invariants.}
\label{fig:tasinv}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{atm}
\end{code}
\caption{[atm.cxl] Withdrawing money from an ATM.}
\label{fig:atm}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{csTAS}
\end{code}
\caption{[csTAS.cxl] Fixed version of Figure~\ref{fig:uplock} using test-and-set.}
\label{fig:tas2}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{UpLock}
\end{code}
\caption{[UpLock.cxl] Program of Figure~\ref{fig:inc} fixed with a lock.}
\label{fig:incfixed}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{RW}
\end{code}
\caption{[RW.cxl] Busy-Waiting Reader/Writer Lock implementation.}
\label{fig:rwbusy}
\end{figure}

\begin{figure}
\begin{code}
\cxlsource{RWtest}
\end{code}
\caption{[RWtest.cxl] Test code for Figure~\ref{fig:rwbusy}.}
\label{fig:rwbusytest}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{RWbusychk}
\end{code}
\caption{[RWbusychk.cxl] Checking for Busy Waiting.}
\label{fig:rwblock}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{RWlock}
\end{code}
\caption{[RWlock.cxl] Reader/Writer with Two Locks.}
\label{fig:rw2lock}
\end{figure}

\begin{figure}
\begin{code}
\cxlsource{RWmulti}
\end{code}
\caption{[RWmulti.cxl] Checking that multiple readers can acquire the read lock.}
\label{fig:rwmulti}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{DinersSema}
\end{code}
\caption{[DinersSema.cxl] Italian Philosophers.}
\label{fig:dinerssema}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{qsort}
\end{code}
\caption{[qsort.cxl] Iterative qsort() implementation.}
\label{fig:qsort}
\end{figure}

\begin{figure}
\begin{code}
\cxlsource{qsorttest}
\end{code}
\caption{[qsorttest.cxl] Test program for Figure~\ref{fig:qsort}.}
\label{fig:qsorttest}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{BBsema}
\end{code}
\caption{[BBsema.cxl] Bounded Buffer implementation using semaphores.}
\label{fig:boundedbuffer}
\end{figure}

\begin{figure}
\begin{code}
\cxlsource{BBsematest}
\end{code}
\caption{[BBsematest.cxl] Test program for Figure~\ref{fig:boundedbuffer}.}
\label{fig:bbtest}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{BBsemadata}
\end{code}
\caption{[BBsemadata.cxl] Test whether the bounded buffer delivers the right data in the
right order.}
\label{fig:BBsemadata}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{gpu}
\end{code}
\caption{[gpu.cxl] A thread-unsafe GPU allocator.}
\label{fig:gpu}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{RWsbs}
\end{code}
\caption{[RWsbs.cxl] Reader/Writer Lock implementation using Split Binary Semaphores.}
\label{fig:RWsplitsema}
\end{figure}

@@

\begin{figure}
\begin{code}
{\small
\cxlsource{RWfair}
}
\end{code}
\caption{[RWfair.cxl] Reader/Writer Lock SBS implementation addressing fairness.}
\label{fig:RWfair}
\end{figure}

@@

\begin{figure}
\begin{code}
{\small
\cxlsource{RWqueue}
}
\end{code}
\caption{[RWqueue.cxl] Reader/Writer Lock SBS implementation using a queue.}
\label{fig:RWqueue}
\end{figure}

\begin{figure}
\begin{code}
\cxlsource{RWqtest}
\end{code}
\caption{[RWqtest.cxl] Test program for Figure~\ref{fig:RWqueue}.}
\label{fig:RWqtest}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{RWcv}
\end{code}
\caption{[RWcv.cxl] Reader/Writer Lock implementation using Mesa-style condition variables.}
\label{fig:RWcv}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{Diners}
\end{code}
\caption{[Diners.cxl] Dining Philosophers.}
\label{fig:diners}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{DinersCV}
\end{code}
\caption{[DinersCV.cxl] Dining Philosophers that grab both forks at the same time.}
\label{fig:dinerscv}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{DinersAvoid}
\end{code}
\caption{[DinersAvoid.cxl] Dining Philosophers that carefully avoid getting into a deadlock
scenario.}
\label{fig:dinersavoid}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{bank}
\end{code}
\caption{[bank.cxl] Bank accounts.}
\label{fig:bank}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{actor}
\end{code}
\caption{[actor.cxl] A producer/consumer actor.}
\label{fig:actor}
\end{figure}

\begin{figure}
\begin{code}
\cxlsource{actortest}
\end{code}
\caption{[actortest.cxl] Test code for producer/consumer actor.}
\label{fig:actortest}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{abp}
\end{code}
\caption{[abp.cxl] Alternating Bit Protocol.}
\label{fig:abp}
\end{figure}

\begin{figure}
\begin{code}
\cxlsource{abptest}
\end{code}
\caption{[abptest.cxl] Test code for alternating bit protocol.}
\label{fig:abptest}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{hw}
\end{code}
\caption{[hw.cxl] Non-blocking queue.}
\label{fig:hw}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{lst1}
\end{code}
\caption{[lst1.cxl] List with non-blocking read operations, part 1.}
\label{fig:lst1}
\end{figure}

\begin{figure}
\begin{code}
\cxlsource{lst2}
\end{code}
\caption{[lst2.cxl] List with non-blocking read operations, part 2.}
\label{fig:lst2}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{barrier}
\end{code}
\caption{[barrier.cxl] Barrier synchronization with semaphores.}
\label{fig:barrier}
\end{figure}

>>>>

\newcommand{\cxllink}[1]{
    [\href{https://www.cs.cornell.edu/home/rvr/cxl/code/#1}{#1}]
}

@@

\begin{figure}
\begin{code}
\cxlsource{triangle}
\end{code}
\caption{\cxllink{triangle.cxl} Computing triangle numbers.}
\label{fig:triangle}
\end{figure}

@@

\begin{figure}[h]
\begin{code}
\cxlsource{Up}
\end{code}
\caption{\cxllink{Up.cxl} Incrementing twice in parallel.}
\label{fig:inc}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{UpEnter}
\end{code}
\caption{\cxllink{UpEnter.cxl} Broken attempt at fixing the code of Figure~\ref{fig:inc}.}
\label{fig:incenter}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{csbarebones}
\end{code}
\caption{\cxllink{csbarebones.cxl} A bare bones critical section with two processes.}
\label{fig:csbarebones}
\end{figure}

\begin{figure}
\begin{code}
\cxlsource{cs}
\end{code}
\caption{\cxllink{cx.cxl} CXL model of a critical section.}
\label{fig:cs}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{naiveLock}
\end{code}
\caption{\cxllink{naiveLock.cxl} Na\"{\i}ve implementation of a shared lock.}
\label{fig:uplock}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{naiveFlags}
\end{code}
\caption{\cxllink{naiveFlags.cxl} Na\"{\i}ve use of flags to solve mutual exclusion.}
\label{fig:upflags}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{naiveTurn}
\end{code}
\caption{\cxllink{naiveTurn.cxl} Na\"{\i}ve use of turn variable to solve mutual exclusion.}
\label{fig:upturn}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{Peterson}
\end{code}
\caption{\cxllink{Peterson.cxl} Peterson's Algorithm}
\label{fig:peterson}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{PetersonInductive}
\end{code}
\caption{\cxllink{PetersonInductive.cxl} Peterson's Algorithm with Inductive Invariant}
\label{fig:petersonproof}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{csonebit}
\end{code}
\caption{\cxllink{csonebit.cxl} Mutual exclusion using a flag per process.}
\label{fig:csonebit}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{PetersonMethod}
\end{code}
\caption{\cxllink{PetersonMethod.cxl} Peterson's Algorithm accessed through methods.}
\label{fig:petersonmethods}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{spinlock}
\end{code}
\caption{\cxllink{spinlock.cxl} Mutual Exclusion using a ``spinlock'' based on test-and-set.}
\label{fig:tas}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{spinlockInv}
\end{code}
\caption{\cxllink{spinlockInv.cxl} Checking invariants.}
\label{fig:tasinv}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{atm}
\end{code}
\caption{\cxllink{atm.cxl} Withdrawing money from an ATM.}
\label{fig:atm}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{csTAS}
\end{code}
\caption{\cxllink{csTAS.cxl} Fixed version of Figure~\ref{fig:uplock} using test-and-set.}
\label{fig:tas2}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{UpLock}
\end{code}
\caption{\cxllink{UpLock.cxl} Program of Figure~\ref{fig:inc} fixed with a lock.}
\label{fig:incfixed}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{RW}
\end{code}
\caption{\cxllink{RW.cxl} Busy-Waiting Reader/Writer Lock implementation.}
\label{fig:rwbusy}
\end{figure}

\begin{figure}
\begin{code}
\cxlsource{RWtest}
\end{code}
\caption{\cxllink{RWtest.cxl} Test code for Figure~\ref{fig:rwbusy}.}
\label{fig:rwbusytest}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{RWbusychk}
\end{code}
\caption{\cxllink{RWbusychk.cxl} Checking for Busy Waiting.}
\label{fig:rwblock}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{RWlock}
\end{code}
\caption{\cxllink{RWlock.cxl} Reader/Writer with Two Locks.}
\label{fig:rw2lock}
\end{figure}

\begin{figure}
\begin{code}
\cxlsource{RWmulti}
\end{code}
\caption{\cxllink{RWmulti.cxl} Checking that multiple readers can acquire the read lock.}
\label{fig:rwmulti}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{DinersSema}
\end{code}
\caption{\cxllink{DinersSema.cxl} Italian Philosophers.}
\label{fig:dinerssema}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{qsort}
\end{code}
\caption{\cxllink{qsort.cxl} Iterative qsort() implementation.}
\label{fig:qsort}
\end{figure}

\begin{figure}
\begin{code}
\cxlsource{qsorttest}
\end{code}
\caption{\cxllink{qsorttest.cxl} Test program for Figure~\ref{fig:qsort}.}
\label{fig:qsorttest}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{BBsema}
\end{code}
\caption{\cxllink{BBsema.cxl} Bounded Buffer implementation using semaphores.}
\label{fig:boundedbuffer}
\end{figure}

\begin{figure}
\begin{code}
\cxlsource{BBsematest}
\end{code}
\caption{\cxllink{BBsematest.cxl} Test program for Figure~\ref{fig:boundedbuffer}.}
\label{fig:bbtest}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{BBsemadata}
\end{code}
\caption{\cxllink{BBsemadata.cxl} Test whether the bounded buffer delivers the right data in the
right order.}
\label{fig:BBsemadata}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{gpu}
\end{code}
\caption{\cxllink{gpu.cxl} A thread-unsafe GPU allocator.}
\label{fig:gpu}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{RWsbs}
\end{code}
\caption{\cxllink{RWsbs.cxl} Reader/Writer Lock implementation using Split Binary Semaphores.}
\label{fig:RWsplitsema}
\end{figure}

@@

\begin{figure}
\begin{code}
{\small
\cxlsource{RWfair}
}
\end{code}
\caption{\cxllink{RWfair.cxl} Reader/Writer Lock SBS implementation addressing fairness.}
\label{fig:RWfair}
\end{figure}

@@

\begin{figure}
\begin{code}
{\small
\cxlsource{RWqueue}
}
\end{code}
\caption{\cxllink{RWqueue.cxl} Reader/Writer Lock SBS implementation using a queue.}
\label{fig:RWqueue}
\end{figure}

\begin{figure}
\begin{code}
\cxlsource{RWqtest}
\end{code}
\caption{\cxllink{RWqtest.cxl} Test program for Figure~\ref{fig:RWqueue}.}
\label{fig:RWqtest}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{RWcv}
\end{code}
\caption{\cxllink{RWcv.cxl} Reader/Writer Lock implementation using Mesa-style condition variables.}
\label{fig:RWcv}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{Diners}
\end{code}
\caption{\cxllink{Diners.cxl} Dining Philosophers.}
\label{fig:diners}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{DinersCV}
\end{code}
\caption{\cxllink{DinersCV.cxl} Dining Philosophers that grab both forks at the same time.}
\label{fig:dinerscv}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{DinersAvoid}
\end{code}
\caption{\cxllink{DinersAvoid.cxl} Dining Philosophers that carefully avoid getting into a deadlock
scenario.}
\label{fig:dinersavoid}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{bank}
\end{code}
\caption{\cxllink{bank.cxl} Bank accounts.}
\label{fig:bank}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{actor}
\end{code}
\caption{\cxllink{actor.cxl} A producer/consumer actor.}
\label{fig:actor}
\end{figure}

\begin{figure}
\begin{code}
\cxlsource{actortest}
\end{code}
\caption{\cxllink{actortest.cxl} Test code for producer/consumer actor.}
\label{fig:actortest}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{abp}
\end{code}
\caption{\cxllink{abp.cxl} Alternating Bit Protocol.}
\label{fig:abp}
\end{figure}

\begin{figure}
\begin{code}
\cxlsource{abptest}
\end{code}
\caption{\cxllink{abptest.cxl} Test code for alternating bit protocol.}
\label{fig:abptest}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{hw}
\end{code}
\caption{\cxllink{hw.cxl} Non-blocking queue.}
\label{fig:hw}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{lst1}
\end{code}
\caption{\cxllink{lst1.cxl} List with non-blocking read operations, part 1.}
\label{fig:lst1}
\end{figure}

\begin{figure}
\begin{code}
\cxlsource{lst2}
\end{code}
\caption{\cxllink{lst2.cxl} List with non-blocking read operations, part 2.}
\label{fig:lst2}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{barrier}
\end{code}
\caption{\cxllink{barrier.cxl} Barrier synchronization with semaphores.}
\label{fig:barrier}
\end{figure}
